---
title: "CompareDedup"
author: "Marc Gauch, David Nowak X3r"
date: "6. Juni 2019"
output:
  ioslides_presentation:
    widescreen: true
    css: styles.css
    includes:
      in_header: TOC_generator.js.wrapper
      self_contained: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Disclaimer 

> - Diese Präsentation wurde mit isoslides erstellt.

> - Isoslides erlaubt kein Inhaltsverzeichnis

> - Es gibt doch eine Lösung

> - Die Aufzeichnis ist nur in Kleinbuchstaben

> - Ich habe das JS angepasst

> - Camel & Pascal Case geht nicht

> - ¯&#92;&#95;(ツ)&#95;/¯

## Inhalt

<!-- add div element table of content for javascript to fill -->
<div id="toc"></div>


## Aufgabenstellung {.section}

> Die Vorstellung der compare.dedup-Funktion im RecordLinkage-Package und potentieller Probleme mit potentiellen Lösungen

## Installation Record Linkage {.section}

Library *RecordLinkage* installieren:
```{r installation, echo=TRUE, message=FALSE, warning=TRUE}
if ("RecordLinkage"  %in% rownames(installed.packages()) == FALSE) {
  install.packages("RecordLinkage")
}
```

Library laden:
```{r echo=TRUE, message=FALSE, warning=FALSE}
library(RecordLinkage)
```

Installierte Version:
```{r echo=TRUE}
packageVersion("RecordLinkage")
```

<div class="notes">
This is my *note*.

- It can contain markdown
- like this list
</div>


## Quellen

Inhaltsverzeichnis
http://rpubs.com/ShKlinkenberg/TOC-for-IOslides-in-Rmarkdown

# Diskussion {.section}

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

<div class="notes">
This is my *note*.

- It can contain markdown
- like this list
</div>

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Slide on two pages

page 1

---

page 2